Examining background gene list issue in clusterProfiler - RNA-seq example

### 2024-09-11 analysis/analyse_rnaseq1.Rmd
thread control for fig 1 and 2

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("kableExtra")
  library("clusterProfiler")
  library("fgsea")
  library("eulerr")
  library("gplots")
  library("parallel")
})

>>>>

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("kableExtra")
  library("clusterProfiler")
  library("fgsea")
  library("eulerr")
  library("gplots")
  library("parallel")
  library("RhpcBLASctl")
})

RhpcBLASctl::blas_set_num_threads(1)
